### 2022-04-18 doc/university-covid.tex
done?

\begin{flushleft}{
	\Large
	\textbf\newline{
		Relative role of community transmission and campus contagion in driving the spread of SARS-CoV-2: lessons from Princeton University
	}
}
\newline
\\ 
\end{flushleft}

@@

Mathematical models have played a crucial role in guiding pandemic responses; university campuses provide a particularly well documented case for institutional outbreaks.
Here, we present descriptive and modeling analyses of SARS-CoV-2 outbreaks on the Princeton University campus---this model was used throughout the pandemic to inform policy decisions for the Princeton University campus.
We demonstrate strong spatiotemporal correlations in epidemic patterns between Princeton University and surrounding communities.
These findings are corroborated by our model predictions, which indicate that the amount of on-campus transmission was likely limited during much of the wider pandemic.

@@

In this study, we analyzed the spread of SARS-CoV-2 on PU campus (\fref{princeton}).
We first begin with a descriptive analysis of the outbreak and then present modeling analyses of the past outbreaks and future scenarios.
PU is located in Mercer County, New Jersey, USA;
the population comprises of 5267 undergraduate students, 2946 graduate students, and 7000 faculty and staff members.
For simplicity, we divided the epidemic into four time periods representing four semesters across two academic years: Fall 2020--2021 (August 24, 2020--January 1, 2021; \fref{princeton}A), Spring 2020--2021 (January 16, 2021--May 14, 2021; \fref{princeton}B), Fall 2021--2022 (August 14, 2021--December 31, 2021; \fref{princeton}C), and Spring 2021--2022 (January 1, 2022--March 18, 2022; \fref{princeton}D).
Throughout the majority of the study period, all students, faculty and staff members who were physically present for more than 8 hours on campus per week were required to participate in asymptomatic testing with varying frequencies.
Asymptomatic individuals submitted self-collected saliva samples, from which the presence of SARS-CoV-2 was tested using Reverse Transcription Polymerase Chain Reaction (RT-PCR).  
Asymptomatic individuals who tested positive were required to isolate for 10 days.
Symptomatic individuals were eligible for rapid PCR tests and had to isolate \swp{Robin and Irini: is self-isolate a better term?} until they received their test results---those who tested positive were required to isolate for at least 10 days after symptom onset and were release 3 days after symptoms resolved.
PCR positives were exempt from asymptomatic testing for 90 days.
Since March 7, 2022, asymptomatic testing frequencies decreased to once a month from once a week for individuals whose vaccine statuses are up-to-date, which in turn likely reduced the accuracy of surveillance; therefore, we chose to focus on epidemic patterns before this change was implemented.
Throughout the study period, contact tracing was also performed for positive cases to quarantine their close contacts, defined as individuals who have been within 6 feet for at least 15 minutes, cumulatively within a 24-hour period.
All data used in this analysis are publicly available on the PU COVID-19 Dashboard website: \url{https://covid.princeton.edu/dashboard}.

@@

In the beginning of the spring semester of the 2020--2021 academic year, the number of cases suddenly increased before classes started (\fref{princeton}B), reflecting $\approx 3000$ undergraduate students returning to campus.
Returning students were required to be tested and quarantine \swp{Robin and Irini: for how long} if they were coming back from CDC-designated states and countries \swp{ask Irini and Robin for details}.
All classes remained virtual, and the testing protocol did not change (twice a week for undergraduate and graduate students, and once a week for faculty and staff members).
The number of cases persisted at similar levels as the fall semester and eventually decreased as classes ended and students went back home---the decrease in the number of cases in PU also coincided with the decrease in the number of cases in Mercer County.
The highest number of cases was reported among faculty and staff members ($=111$), followed by undergraduate students ($=101$), and graduate students ($=29$).

For the fall semester of the 2021--2022 academic year, all students and faculty and staff members were required to be vaccinated \swp{with two doses? need to ask Robin and Irini} with a very few medical and religious exemptions.
By the beginning of the semesters, ??\% of students and ??\% of faculty and staff members were vaccinated \swp{ask Robin and Irini}.
% As of January 11th, 99\% of undergraduate students, 98\% of graduate students, and 96\% of faculty and staff members were vaccinated.
Vaccinees were required to be tested once a week, while unvaccinated individuals were required to be tested twice a week.
In-person classes and social events fully resumed on campus while all individuals were required to wear masks indoors with a few exceptions (e.g., when eating or drinking, or when teaching a small class).
The number of cases remained similar to previous semesters until November when the number of cases began to increase primarily among undergraduate students around Thanksgiving (\fref{princeton}C).  
In order to prevent transmission, testing frequency was increased to twice a week for undergraduate students on November 27th, 2021; the size of non-academic gatherings were also limited to 20 people.
The number of cases decreased slightly as classes ended but soon increased back up as the Omicron (BA.1) variant began to spread on campus and in Mercer county.

@@

Transmission processes are modeled by first setting the contact reproduction number $\Rc$, which we define as the average number of infectious contacts an infected individual would make throughout the course of their infection;
here, infectious contacts refer to contacts that would result in infection when the contactee (i.e., the contacted individual) is susceptible to infection.
The contact reproduction number implicitly accounts for all intervention measures that we do not model explicitly, such as social distancing and contact tracing---in other words, this contact reproduction number does not account for asymptomatic testing or vaccination, which are modeled separately.
We further decompose $\Rc$ into pre-symptomatic $\mathcal R_p = \beta_p D_p$ and (a)symptomatic $\mathcal R_s = \beta_s D_s$ reproduction numbers, where $\beta_p$ and $\beta_s$ represent the corresponding infectious contact rates during pre-symptomatic and (a)symptomatic stages, respectively. Pre-symptomatic and (a)symptomatic reproduction numbers are calculated based on the assumed value of the proportion of presymptomatic transmission $p_p = 0.5$: $\mathcal R_p/\mathcal R_s = p_p/(1 - p_p)$.
On each day, all infected individuals who have not yet been isolated then make infectious contacts at random to anyone on campus; the number of infectious contacts are drawn from a negative binomial distribution with a mean of either $\beta_p$ or $\beta_s$ and an overdispersion parameter of $k=0.1$ to account for the possibility of super-spreading events \citep{10.12688/wellcomeopenres.15842.3}.
Infectious contacts from local community can be also made at random to anyone on campus; these contacts are modeled using a Poisson distribution with a time-varying mean, which is calculated by scaling the daily number of cases by $\theta$ and shifting it by 1 week to account for reporting delays.
Infectious contacts, whether made by individuals on campus or from outside, result in infection only when the contacted individuals are susceptible; when the contacted individuals are vaccinated, and therefore partially susceptible to infection, they have a reduced probability of infection corresponding to their susceptibility (discussed later).

@@

Epidemiological and interventions conditions changed throughout the spring semester of the 2021--2022 academic year.
We therefore extend to model to account for more realistic settings and focus on the outbreak patterns among undergraduate students.
First, based on \citep{ferguson2021report}, we assume that two and three doses of vaccines reduce susceptibility against the Omicron variant by 10\% and 70\%, respectively. 
We also assume that the transmissibility of Omicron is reduced proportionally following previously assumed 90--to--20 ratio for the Delta variant;
in other words, two and three doses of  vaccines reduce transmissibility by 2.2\% and 15.6\%, respectively.
The immunity from the third dose is assumed to take 7 days to develop and wane at the same rate as before (in this case, 70\% to 39\% in 20 weeks).
Finally, the isolation period is reduced to 5 days.

@@

\begin{figure}[!thp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_omicron_spring.pdf}
\caption{
\textbf{The impact of changes in testing frequency and an increased reproduction number on the spread of the Omicron variant.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
}
\label{fig:omicron1}
\end{figure}

@@

Although previous outbreak reports from other universities primarily focused on transmission on university campuses \citep{wilson2020multiple,currie2021interventions}, a few studies identified off-campus infections as an important source of transmission \citep{fox2021response,hamer2021assessment}.
For example, extensive modeling efforts from Cornell University demonstrated an increase in the amount of transmission from outside the university campus during fall 2021 and found that community transmissions are the biggest risk for faculty and staff members \citep{frazier2022modeling}.
Our study further extends these findings in demonstrating a strong spatiotemporal correlation in the spread of SARS-CoV-2 between university campuses and surrounding communities.
Our analysis suggest that comparing the ratios between the cases on university campuses and neighboring communities can also provide a useful measure for how well a university campus is controlling the epidemic; 
however, we note that this ratio needs to be interpreted with caution as it is sensitive to changes in testing patterns.
Future studies may combine phylogenetic data to better understand spatial patterns of SARS-CoV-2 on campus.

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton/figure_princeton_correlation2.pdf}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in Mercer County stratified by subpopulations.}
Points represent the number of reported cases.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
}
\end{figure}

@@

\begin{figure}[!htp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figure_princeton/figure_princeton_map.pdf}
\end{center}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in counties in New Jersey.}
(A--C) Map of correlations between the weekly number of cases in PU and in counties in New Jersey.
(D--F) Relationship between case correlations and distance from Mercer County.
Points represent the estimated correlation coefficients.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
Black points and lines represent correlations based on all cases in PU.
Red points and lines represent correlations based on cases among faculty and staff members in PU.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton/figure_princeton_newyork.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in PU and New York City.}
(A--C) Epidemic trajectories across three semesters: Fall 2020 (A), Spring 2020 (B), and Fall 20201 (C).
Colored bar plots represent the weekly number of cases from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases in New York City.
(D--F) Correlations between the weekly number of cases in PU and in New York City.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton/figure_princeton_phil.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in PU and Philadelphia.}
(A--C) Epidemic trajectories across three semesters: Fall 2020 (A), Spring 2020 (B), and Fall 20201 (C).
Colored bar plots represent the weekly number of cases from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases in Philadelphia.
(D--F) Correlations between the weekly number of cases in PU and in Philadelphia.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton/figure_princeton_map_extended.pdf}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in counties in New Jersey, Pennsylvania, and New York State.}
(A--C) Map of correlations between the weekly number of cases in PU and in counties in New Jersey, Pennsylvania, and New York State.
(D--F) Relationship between case correlations and distance from Mercer County.
Points represent the estimated correlation coefficients.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
Black points and lines represent correlations based on all cases in PU.
Red points and lines represent correlations based on cases among faculty and staff members in PU.
New York City is excluded from this analysis as the data provided by New York Times are not further stratified by county levels.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton/figure_princeton_simulation_nowaning.pdf}
\caption{
\textbf{Comparisons between model predictions and the observed numbers of cases for fall 2021 without immunity waning.}
Points represent the weekly number of reported cases in PU.
Red lines and shaded areas represent median model predictions and 90\% quantiles across 100 simulations.
See figure 2 in the main text for details.
}
\end{figure}

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Relative role of community transmission and campus contagion in driving the spread of SARS-CoV-2: lessons from Princeton University
	}
}
\newline
\\
Sang Woo Park\textsuperscript{1}
Irini Daskalaki\textsuperscript{?}
Robin M. Izzo\textsuperscript{?}
C. Jessica E. Metcalf\textsuperscript{1}
Daniel A. Notterman\textsuperscript{?}
Bryan T.\ Grenfell\textsuperscript{1}
\\
\bigskip
\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\bigskip

Corresponding author: ???
\bigskip
\end{flushleft}

@@

Mathematical models have played a crucial role in guiding pandemic responses, espeicially among higher education institutions. University campuses further present a particularly well-documented case for institutional outbreaks, thereby providing a unique opportunity to understand detailed patterns of pathogen spread.
Here, we present descriptive and modeling analyses of SARS-CoV-2 outbreaks on the Princeton University campus---this model was used throughout the pandemic to inform policy decisions for the Princeton University campus.
We demonstrate strong spatiotemporal correlations in epidemic patterns between the Princeton University campus and surrounding communities.
These findings are corroborated by our model predictions, which indicate that the amount of on-campus transmission was likely limited during much of the wider pandemic until the end of 2021.
Finally, we find that a super-spreading event played a major role in driving the recent outbreak on the Princeton University campus during the spring semester of the 2021--2022 academic year.
Despite large numbers of cases on campus, case levels in surrounding communities remained low, suggesting that there was little to no spillover transmission from campus to the local community.

@@

In this study, we analyzed the spread of SARS-CoV-2 on PU campus (\fref{princeton}).
We first begin with a descriptive analysis of the outbreak and then present modeling analyses of the past outbreaks and future scenarios.
PU is located in Mercer County, New Jersey, USA;
the population comprises of 5267 undergraduate students, 2946 graduate students, and 7000 faculty and staff members.
For simplicity, we divided the epidemic into four time periods representing four semesters across two academic years: Fall 2020--2021 (August 24, 2020--January 1, 2021; \fref{princeton}A), Spring 2020--2021 (January 16, 2021--May 14, 2021; \fref{princeton}B), Fall 2021--2022 (August 14, 2021--December 31, 2021; \fref{princeton}C), and Spring 2021--2022 (January 1, 2022--March 18, 2022; \fref{princeton}D).
Throughout the majority of the study period, all students, faculty and staff members who were physically present for more than 8 hours on campus per week were required to participate in asymptomatic testing with varying frequencies.
Asymptomatic individuals submitted self-collected saliva samples, from which the presence of SARS-CoV-2 was tested using Reverse Transcription Polymerase Chain Reaction (RT-PCR).  
Those who tested positive were required to isolate for at least 10 days after symptom onset or test date (whichever was longer) and were released when they had been at least 48 hours with improving or resolving symptoms as per New Jersey Department of Health guidance.
PCR positives were exempt from asymptomatic testing for 90 days.
Since March 7, 2022, asymptomatic testing frequencies decreased to once a month from once a week for individuals whose vaccine statuses are up-to-date, which in turn likely reduced the accuracy of surveillance; therefore, we chose to focus on epidemic patterns before this change was implemented.
Throughout the study period, contact tracing was also performed for positive cases to alert their close contacts to either quarantine or test more frequently according to the close contacts' vaccination status, and to gather data that could help uncover clusters of transmission or superspreader events.
All data used in this analysis are publicly available on the PU COVID-19 Dashboard website: \url{https://covid.princeton.edu/dashboard}.

@@

In the beginning of the spring semester of the 2020--2021 academic year, the number of cases suddenly increased before classes started (\fref{princeton}B), reflecting $\approx 3000$ undergraduate students returning to campus.
Returning students were required to be tested and quarantine for 7 days regardless of their returning location.
All classes remained virtual, and the testing protocol did not change (twice a week for undergraduate and graduate students, and once a week for faculty and staff members).
The number of cases persisted at similar levels as the fall semester and eventually decreased as classes ended and students went back home---the decrease in the number of cases in PU also coincided with the decrease in the number of cases in Mercer County.
The highest number of cases was reported among faculty and staff members ($=111$), followed by undergraduate students ($=101$), and graduate students ($=29$).

For the fall semester of the 2021--2022 academic year, all students and faculty and staff members were required to be vaccinated with a very few medical and religious exemptions.
By the beginning of the semesters, ??\% of students and ??\% of faculty and staff members were vaccinated \swp{ask Robin and Irini}.
% As of January 11th, 99\% of undergraduate students, 98\% of graduate students, and 96\% of faculty and staff members were vaccinated.
Vaccinees were required to be tested once a week, while unvaccinated individuals were required to be tested twice a week.
In-person classes and social events fully resumed on campus while all individuals were required to wear masks indoors with a few exceptions (e.g., when eating or drinking, or when teaching a small class).
The number of cases remained similar to previous semesters until November when the number of cases began to increase primarily among undergraduate students around Thanksgiving (\fref{princeton}C).  
In order to prevent transmission, testing frequency was increased to twice a week for undergraduate students on November 27th, 2021; the size of non-academic gatherings were also limited to 20 people.
The number of cases decreased slightly as classes ended but soon increased back up as the Omicron (BA.1) variant began to spread on campus and in Mercer county.

@@

Transmission processes are modeled by first setting the contact reproduction number $\Rc$, which we define as the average number of infectious contacts an infected individual would make throughout the course of their infection;
here, infectious contacts refer to contacts that would result in infection when the contacted individual is susceptible to infection.
The contact reproduction number implicitly accounts for all intervention measures that we do not model explicitly, such as social distancing and contact tracing---in other words, this contact reproduction number does not account for asymptomatic testing or vaccination, which are modeled separately.
We further decompose $\Rc$ into pre-symptomatic $\mathcal R_p = \beta_p D_p$ and (a)symptomatic $\mathcal R_s = \beta_s D_s$ reproduction numbers, where $\beta_p$ and $\beta_s$ represent the corresponding infectious contact rates during pre-symptomatic and (a)symptomatic stages, respectively. Pre-symptomatic and (a)symptomatic reproduction numbers are calculated based on the assumed value of the proportion of presymptomatic transmission $p_p = 0.5$: $\mathcal R_p/\mathcal R_s = p_p/(1 - p_p)$.
On each day, all infected individuals who have not yet been isolated then make infectious contacts at random to anyone on campus; the number of infectious contacts are drawn from a negative binomial distribution with a mean of either $\beta_p$ or $\beta_s$ and an overdispersion parameter of $k=0.1$ to account for the possibility of super-spreading events \citep{10.12688/wellcomeopenres.15842.3}.
Infectious contacts from local community can be also made at random to anyone on campus; these contacts are modeled using a Poisson distribution with a time-varying mean, which is calculated by scaling the daily number of cases by $\theta$ and shifting it by 1 week to account for reporting delays.
Infectious contacts, whether made by individuals on campus or from outside, result in infection only when the contacted individuals are susceptible; when the contacted individuals are vaccinated, and therefore partially susceptible to infection, they have a reduced probability of infection corresponding to their susceptibility (discussed later).

@@

Epidemiological and interventions conditions changed throughout the spring semester of the 2021--2022 academic year.
We therefore extend to model to account for more realistic settings and focus on the outbreak patterns among undergraduate students.
First, based on \citep{ferguson2021report}, we assume that two and three doses of vaccines reduce susceptibility against the Omicron variant by 10\% and 70\%, respectively. 
We also assume that the transmissibility of Omicron is reduced proportionally following previously assumed 90--to--20 ratio for the Delta variant;
in other words, two and three doses of vaccines reduce transmissibility by 2.2\% and 15.6\%, respectively.
The immunity from the third dose is assumed to take 7 days to develop \citep{moreira2022safety} and wane at the same rate as before (in this case, 70\% to 39\% in 20 weeks).
Finally, the isolation period is reduced to 5 days.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_omicron_spring.pdf}
\caption{
\textbf{The impact of changes in testing frequency and an increased reproduction number on the spread of the Omicron variant.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
}
\label{fig:omicron1}
\end{figure}

@@

Although previous outbreak reports from other universities primarily focused on transmission on university campuses \citep{wilson2020multiple,currie2021interventions}, a few studies identified off-campus infections as an important source of transmission \citep{fox2021response,hamer2021assessment}.
For example, extensive modeling efforts from Cornell University demonstrated an increase in the amount of transmission from outside the university campus during fall 2021 and found that community transmissions are the biggest risk for faculty and staff members \citep{frazier2022modeling}.
Our study further extends these findings in demonstrating a strong spatiotemporal correlation in the spread of SARS-CoV-2 between university campuses and surrounding communities.
Our analysis suggest that comparing the ratios between the cases on university campuses and neighboring communities can also provide a useful measure for how well a university campus is controlling the epidemic; 
however, we note that this ratio needs to be interpreted with caution as it is sensitive to changes in testing patterns as well as the numbers of students on campus.
For example, the ratios of cases can suddenly change during holidays when students are away from campus.
Future studies may combine phylogenetic data to better understand spatial patterns of SARS-CoV-2 on campus.

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_correlation2.pdf}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in Mercer County stratified by subpopulations.}
Points represent the number of reported cases.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
}
\end{figure}

@@

\begin{figure}[!htp]
\begin{center}
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_map_new.pdf}
\end{center}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in counties in New Jersey.}
(A--C) Map of correlations between the weekly number of cases in PU and in counties in New Jersey.
(D--F) Relationship between case correlations and distance from Mercer County.
Points represent the estimated correlation coefficients.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
Black points and lines represent correlations based on all cases in PU.
Red points and lines represent correlations based on cases among faculty and staff members in PU.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_newyork_new.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in PU and New York City.}
(A--C) Epidemic trajectories across three semesters: Fall 2020 (A), Spring 2020 (B), and Fall 20201 (C).
Colored bar plots represent the weekly number of cases from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases in New York City.
(D--F) Correlations between the weekly number of cases in PU and in New York City.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_philly_new.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in PU and Philadelphia.}
(A--C) Epidemic trajectories across three semesters: Fall 2020 (A), Spring 2020 (B), and Fall 20201 (C).
Colored bar plots represent the weekly number of cases from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases in Philadelphia.
(D--F) Correlations between the weekly number of cases in PU and in Philadelphia.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=0.8\textwidth]{../figure_princeton_new/figure_princeton_map_extended.pdf}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in counties in New Jersey, Pennsylvania, and New York State.}
(A--C) Map of correlations between the weekly number of cases in PU and in counties in New Jersey, Pennsylvania, and New York State.
(D--F) Relationship between case correlations and distance from Mercer County.
Points represent the estimated correlation coefficients.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
Black points and lines represent correlations based on all cases in PU.
Red points and lines represent correlations based on cases among faculty and staff members in PU.
New York City is excluded from this analysis as the data provided by New York Times are not further stratified by county levels.
}
\end{figure}

@@

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_nowaning.pdf}
\caption{
\textbf{Comparisons between model predictions and the observed numbers of cases for fall 2021 without immunity waning.}
Points represent the weekly number of reported cases in PU.
Red lines and shaded areas represent median model predictions and 90\% quantiles across 100 simulations.
See figure 2 in the main text for details.
}
\end{figure}
